Outline

### 2023-04-20 manuscript/outline.Rmd
Updating outline with figure notes from Frank

@@

@@

@@

Remember to add Pearson and Spearmen correlation coefficients in the corners!

@@

>>>>

Include the descriptor for what "FTXXXX" means.

Note that these were taken from the MESOSCOPE dataset.

Explain the chromatograms (RT/int/ what "goodness" requires?)

Explain that we grabbed the center of the peak +/- 1 (2?) minutes

@@

Explain what the different datasets are?

@@

Dark blue and dark green are too similar, need to separate these better somehow.

Include conclusions in figure legend? Something like "slope of the line is much greater in All metrics and XCMS metrics, indicating overfitting"?

@@

Remember to add Pearson and Spearman correlation coefficients in the corners!

@@

Explain why there are no values for GPF in Pttime/CultureData?
